Data Specialization for a Staged Lambda Calculus

### 2015-02-28 paper/appendix.tex
working on trie
trie input code

\begin{lstlisting} 
datatype letter = A | B | C
datatype string = EmptyS | ConsS of letter * string
datatype list = EmptyL | ConsL of string * list
/* helper function */
fun partition (l : list) : (bool * list * list * list) =
 case l of
   EmptyL => (false,EmptyL,EmptyL,EmptyL)
 | ConsL (s,ss) =>
     let (anyEmpty,a,b,c) = partition ss in
     case unroll s of
       EmptyS => (true,a,b,c)
     | ConsS (z,zs) =>
         case z of 
           A => (anyEmpty, ConsL(zs,a), b, c) 
         | B => (anyEmpty, a, ConsL(zs,b), c) 
         | C => (anyEmpty, a, b, ConsL(zs, c))
fun exists ((l,s) : list * $string) : $bool =
 case l of 
   EmptyL => next{false} 
 | ConsL _ => 
   let (anyEmpty, a, b, c) = partition l in
   next {
     case prev{s} of
       EmptyS => prev{
         if anyEmpty then next{true} else next{false}
         }
     | ConsS (z,zs) =>
         case z of
           A => prev{exists (a,next{zs})}
         | B => prev{exists (b,next{zs})} 
         | C => prev{exists (c,next{zs})}
   }
\end{lstlisting}

>>>>

\begin{lstlisting} 
atsignmono { 
datatype letter = A | B | C 
datatype string = EmptyS | ConsS of letter * string
datatype list   = EmptyL | ConsL of string * list

fun partition (EmptyL) = (false,EmptyL,EmptyL,EmptyL) 
| partition (ConsL (s,ss)) = 
  let val (anyEmpty,a,b,c) = partition ss in 
  case s of 
    EmptyS => (true,a,b,c) 
  | ConsS (A,z) => (anyEmpty,ConsL(z,a),b,c) 
  | ConsS (B,z) => (anyEmpty,a,ConsL(z,b),c) 
  | ConsS (C,z) => (anyEmpty,a,b,ConsL(z,c)) 
}
atsignnext { 
datatype letter2 = A2 | B2 | C2
datatype string2 = EmptyS2 | ConsS2 of letter2 * string2
}

fun exists (mono{EmptyL},next{s}) = next{false} 
  | exists (mono{ConsL ht},next{s}) = 
	let atsignmono{
	  val (anyEmpty,a,b,c) = partition (ConsL ht)
	} in next { 
	case s of 
	  EmptyS2 => prev{hold mono{anyEmpty}} 
	| ConsS2 (A2,z) => prev{exists(mono{a},next{z})} 
	| ConsS2 (B2,z) => prev{exists(mono{b},next{z})}
	| ConsS2 (C2,z) => prev{exists(mono{c},next{z})}  
	} 
\end{lstlisting}
